Integration of Multiple Constraints in ACG

### 2013-09-22 lenls/paper.tex
LENLS: Finishing the Conclusion

We have considered the problem of building a wide-coverage ACG, specifically
the problem of expressing a multitude of linguistic constraints. We have
examined previous techniques and found no satisfying solution. We have thus
provided an extension of the ACG formalism to solve the problem and justified
the need for the increased expressivity. This embedding of syntactic
constraints will be used to define a syntax-semantics interface and then to
build discourse structures.

In the end, this lets us define the syntax in a clean way using the idiomatic
style of categorial grammars (simple atomic types like $N$, $NP$ and $S$) and
then define the constraints themselves the same way as they are defined in
papers which try to formalize them individually (such as is the case with
\cite{pogodalla2012controlling}).

>>>>

We have considered the problem of building a wide-coverage ACG, specifically
the problem of expressing a multitude of linguistic constraints. We have
examined previous techniques and found no satisfying solution. We have thus
provided an extension of the ACG formalism to solve the problem and justified
the need for the increased expressivity. This embedding of syntactic
constraints will contribute to an effort to define a syntax-semantics
interface and later to build discourse structures.

In the end, our approach us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$, $NP$ and
$S$) and then define the constraints themselves the same way as they are
defined in ACG research (such as is the case with
\cite{pogodalla2012controlling}).

Interesting avenues of future work include: digging deeper into the
language-theoretical properties of G-ACGs (Are ACG object languages closed on
intersection? Are pangraphical languages expressible as extrinsic languages?),
searching for a metagrammatical description of constraint signatures to ease
work on G-ACG grammars and finally building large-scale grammars to verify the
utility of our approach.
